Learning can mediate the evolution of\\ (cheap and costly) signals of quality

### 2020-11-03 Presentations/GenesAsEnviron.tex
New file with the code for the AGA present. figures. New files using cluster analysis to classify inds withon populations. cpp modified to run also replicates serially, or parallely externally. Improved some of the plots.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
October 26, 2020}

@@

\begin{block}{The need partners with actions}

@@

@@

@@

\begin{center}\includegraphics[width=0.7\linewidth]{../Images//pavlov} \end{center}

@@

\hypertarget{associative-learning}{%
\section{Associative learning}\label{associative-learning}}

\begin{frame}{Reinforcement learning theory}
\protect\hypertarget{reinforcement-learning-theory}{}

\begin{columns}[T]
 \column{0.5\linewidth}
 \begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
  \end{equation*}
  \pause
  \includegraphics[width=1\textwidth]{../Images//learn_curve.png}
 \column{0.5\linewidth}
  \pause
  \includegraphics[height=.9\textheight]{../Images//predErrorNeur.png}
\end{columns}

@@

\begin{frame}{Reinforcement learning theory}
\protect\hypertarget{reinforcement-learning-theory-1}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//learnUpdate} \end{center}

@@

\begin{frame}{The Hawk-Dove game}
\protect\hypertarget{the-hawk-dove-game}{}

Individuals have one of two genetically determined phenotypic
strategies. \emph{Hawks} are willing to start a conflict over resources,
while \emph{doves} prefer to stand down in the hope to share the
resource without an aggressive contest.

\begin{center}\includegraphics[width=0.5\linewidth]{../Images//HDgame} \end{center}

@@

\begin{frame}{The hawk-dove game}
\protect\hypertarget{the-hawk-dove-game-1}{}

\begin{align*}
w_H &= p_H \frac{V-C}{2}+(1-p_h) V\\
w_D &= p_H 0 + (1-p_H)\frac{V}{2}
\end{align*} \vspace{-0.8cm}

\begin{center}\includegraphics[width=0.55\linewidth]{../Images//Hawk_dove_plot} \end{center}

@@

\begin{frame}{Environmental states}
\protect\hypertarget{environmental-states}{}

\begin{block}{Discrete states}

\includegraphics[width=0.8\textwidth]{../Images//discreteStates.png}

@@

\begin{block}{Continuos states}

\includegraphics[width=0.8\textwidth]{../Images//contStates.png}

@@

\begin{frame}{Continuos environmental states}
\protect\hypertarget{continuos-environmental-states}{}

\begin{equation*}
  \Delta V_{t(s)}=\alpha \underbrace{(R_t-V_t)}_\text{prediction error}
\end{equation*}

\begin{figure}
\includegraphics[width=0.6\linewidth]{../Images/cartoonRBF} \caption{\label{fig:learning_cartoonRBF}Function approximation for the actor and the critic. Using random values for the responses of each center. Circles show the location of the centers and the maximum response they trigger, while the lines show the total response along the badge size continium.}\label{fig:fig2}
\end{figure}

\hypertarget{our-model}{%
\section{Our model}\label{our-model}}

\begin{frame}{The hawk-dove game 2.0}
\protect\hypertarget{the-hawk-dove-game-2.0}{}

\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{1cm} | >{\centering\arraybackslash}p{4.5cm} | >{\centering\arraybackslash}p{4.5cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-10-1} \end{center}

\begin{frame}{Sender Code}
\protect\hypertarget{sender-code}{}

\begin{equation*}
s_i = \frac{1}{1+e^{-(\epsilon_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-11-1} \end{center}

\begin{frame}{Receiver code}
\protect\hypertarget{receiver-code}{}

\begin{equation*}
  \Delta V_{t(s)}=\alpha (R_t-V_t)
\end{equation*}

\begin{center}\includegraphics[width=0.6\linewidth]{../Images/cartoonRBF} \end{center}

@@

Learning simulations (without evolution yet), the sender code is set as
an honest signal. Receivers develop a threshold like response according
to their quality

@@

@@

\begin{block}{Variation among replicates}

set of simulations with the badge working as a handicap (cost inversely
proportional to quality)

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDynAll_betCost5} \end{center}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status-1}{}

\begin{block}{Individual replicates: Badges}

One of the replicates of the previous slide, the badge as a handicap

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status-2}{}

\begin{block}{Individual replicates: Badges}

Panels show the changes in frequency distribution along evolution
(\(\alpha\), \(\beta\), and resulting badge respectively) for the
replicate shown in the previous slide

\includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistAlpha0_betCost5} \includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistBeta0_betCost5} \includegraphics[height=0.28\textheight]{../Simulations/betCostEvol1_/evolDistBadge0_betCost5} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-16}
\end{figure}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status-3}{}

@@

One of the replicates where the badge did not evolve

@@

\begin{frame}{The effect of costs on Badges of Status}
\protect\hypertarget{the-effect-of-costs-on-badges-of-status}{}

@@

Colours correspond to replicates, each point is one snapshot on the
second half of the simulations. Higher costs seem to favour the
signalling equilibrium

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/betCostEvol1_/BehavIntALL} \end{center}

\begin{frame}{The effect of costs on Badges of Status}
\protect\hypertarget{the-effect-of-costs-on-badges-of-status-1}{}

\begin{block}{Badge size}

Same as previous slide but for the resulting signal. Higher costs yield
smaller averga sizes and smaller ranges.

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/betCostEvol1_/CueALL} \end{center}

@@

\begin{block}{Variation among replicates}

Here simulations where the signal has no cost

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/nIntGroupEvol1_/evolDynALL_nIntGroup2000} \end{center}

@@

\begin{block}{Variation within a replicate}

Here simulations where the signal has no cost.

There seems to be some consistency in the three type of sender codes

\begin{center}\includegraphics[width=0.8\linewidth]{../Simulations/nIntGroupEvol1_/evolDyn8_nIntGroup2000} \end{center}

@@

\begin{block}{Variation within a replicate}

Panels show the changes in frequency distribution along evolution
(\(\alpha\), \(\beta\), and resulting badge respectively) for the
replicate shown in the previous slide

Branching events in the reaction norm parameters yield three types of
sender codes. One (more or less) honest, two dishonest (one with a big
badge and one with a small badge)

\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistAlpha8_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistBeta8_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol1_/evolDistBadge8_nIntGroup2000} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-22}
\end{figure}

@@

Values of \(\alpha\) and \(\beta\) for each individual in the different
replicates. Each dot an individual, each panel a replicate. Individuals
are sampled from populations from the second half of the simulations.

Individuals in some simulations split up in three groups, others in two
groups; in one simulation the population does not split up

\begin{frame}{The evolution of cheap Badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status-4}{}

@@

\begin{frame}{Interaction structures - do they matter?}
\protect\hypertarget{interaction-structures---do-they-matter}{}

\begin{center}\includegraphics[width=1\linewidth]{../Images/networks} \end{center}

(Chaine et al. 2018)

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures}{}

Behavioural interactions and badge size for simulations with costs where
individuals interact in small groups. On the \(x\) axes number of
different individuals each focal interacts with.

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCost_/BehavIntALL} \includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCost_/CueALL} \end{center}

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures-1}{}

\begin{block}{Cheap signals (free)}

Variation among individuals in different replicates (just like before)
in replicates where individuals interact with 10 other individuals.

A part from replicates with two clusters, the clustering seems less
straightforward as before

\begin{center}\includegraphics[width=0.85\linewidth]{../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup10} \end{center}

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures-2}{}

\begin{block}{Cheap signals (free)}

Behavioural interactions for the replicates form previous slide. I split
up the replicates according to clusters (despite clusters not being
clear cut).

Only replicates with only one cluster seems to have less aggressive
interactions

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup10} \end{center}

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures-3}{}

\begin{block}{Cheap signals or Individual recognition?}

In these set, I changed the learning set up, I increased the number of
centers (10 now, 6 before) along the signal axis; and I reduced the
level or generalization.

There seems to be an effect on the slope of the reaction norm. It stays
very close to zero.

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCenters1_/evolDynALL_nIntGroup10} \end{center}

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures-4}{}

\begin{block}{Cheap signals or Individual recognition}

Same replicates as the previous slide. Variation in \(\beta\) and
\(\alpha\) among individuals for different replicates.

No clear clustering. Variation mostly along the \(\alpha\) axis

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupCenters1_/corrAlphBet_nIntGroup10} \end{center}

\begin{frame}{Localized interaction structures}
\protect\hypertarget{localized-interaction-structures-5}{}

\begin{block}{Cheap signals or Individual recognition?}

Panels show the changes in frequency distribution along evolution
(\(\alpha\), \(\beta\), and resulting badge respectively) for the
replicate shown in the previous slide.

\(\beta\) around zero, \(\alpha\) all over the place.

\begin{flushleft}\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistAlpha5_nIntGroup10} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistBeta5_nIntGroup10} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupCenters1_/evolDistBadge5_nIntGroup10} \end{flushleft}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-chaine_Manipulating_2018}{}%
Chaine, Alexis S., Daizaburo Shizuka, Theadora A. Block, Lynn Zhang, and
Bruce E. Lyon. 2018. ``Manipulating Badges of Status Only Fools
Strangers.'' \emph{Ecology Letters} 21 (10): 1477--85.
\url{https://doi.org/10.1111/ele.13128}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
November 02, 2020}

@@

\begin{block}{The need to match partners with actions}

@@

(Botero et al. 2010)

@@

\begin{frame}{Are bibs really badges?}
\protect\hypertarget{are-bibs-really-badges}{}

\begin{flushleft}\includegraphics[width=0.3\linewidth]{../Images/Sanchez-Tojar_2018} \end{flushleft}

@@

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_0} \end{center}

@@

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-1}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_1} \end{center}

@@

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-2}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_2} \end{center}

@@

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-3}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_3} \end{center}

@@

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-4}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_5} \end{center}

@@

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-5}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_6} \end{center}

\begin{frame}{A model of communication in animal conflict}
\protect\hypertarget{a-model-of-communication-in-animal-conflict}{}

\vspace{-0.5cm}

\begin{block}{Comunication}

\begin{columns}[T]

\column{0.45\linewidth}

The sender code

\tiny
\begin{equation*}
B_i = \frac{1}{1+e^{-(\textcolor{red}{\alpha_s} +\textcolor{red}{\beta_s} Q_i)}}
\end{equation*}

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-19-1} \end{center}

\column{0.45\linewidth}

The receiver code (learning)

\tiny
\begin{equation*}
  \Delta V_{t(s)}=\alpha (R_t-V_t)
\end{equation*}

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-20-1} \end{center}

\end{columns}

@@

\begin{block}{Conflict}

\vspace{0.3cm}
\begin{columns}
\column{0.5\linewidth}
hawk-dove game
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.2cm} | >{\centering\arraybackslash}p{2.5cm} | >{\centering\arraybackslash}p{0.8cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

\column{0.5\linewidth}

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-21-1} \end{center}

\end{columns}

@@

@@

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}

@@

@@

@@

\begin{frame}{Badges of Status: do they matter?}
\protect\hypertarget{badges-of-status-do-they-matter}{}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/compClustRep_betCost5} \end{center}

--\textgreater{} --\textgreater{} --\textgreater{}

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol4_/evolDyn13_nIntGroup2000} \end{center}

@@

\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistAlpha13_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistBeta13_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistBadge13_nIntGroup2000} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-27}
\end{figure}

@@

@@

@@

--\textgreater{}

--\textgreater{}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-botero_Evolution_2010}{}%
Botero, C. A, I. Pen, J. Komdeur, and F. J Weissing. 2010. ``The
Evolution of Individual Variation in Communication Strategies.''
\emph{Evolution} 64 (11): 3123--33.
